\documentclass[a4paper,11pt]{article}

% --- Packages ---
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{margin=0.8in}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\begin{document}


    \begin{center}
    {\LARGE \textbf{Sanjiv Raghunandan}} \\
    \href{mailto:sanjivrnandan@gmail.com}{sanjivrnandan@gmail.com} \quad | \quad +91 98808 77662 \\
    \href{https://www.linkedin.com/in/sanjiv-raghunandan-38b868321}{Linkedin} \quad | \quad \href{https://github.com/sanjiv-raghunandan}{GitHub}
    \end{center}

\vspace{5pt}


% --- Summary ---
\textbf{SUMMARY}
\vspace{3pt}
\hrule
\vspace{1pt}
Final year Computer Science student specializing in software development, artificial intelligence, machine learning, distributed systems, and computer networking. Skilled in taking ideas from concept to reality by building robust, scalable applications. Looking for internships and full-time roles.

% --- Education ---
\textbf{EDUCATION}
\vspace{3pt}
\hrule
\vspace{1pt}
\textbf{B.Tech in Computer Science} | PES University, Bengaluru \hfill \textbf{2022 – Present} \\
- Awarded scholarship for achieving distinction

% --- Skills ---
\textbf{SKILLS}
\vspace{3pt}
\hrule
\vspace{1pt}
\textbf{Languages:} Python, C, Java, Go, JavaScript, R, SQL \\
\textbf{Tools \& Technologies:} Git, Docker, Wireshark, Cisco Packet Tracer \\
\textbf{Relevant Coursework:} Software Engineering, Machine Learning, Database Management Systems, Computer Networks, BlockChain, Network Security, Cloud Computing, Object Oriented Programming

% --- Experience ---
\textbf{EXPERIENCE}
\vspace{3pt}
\hrule
\vspace{1pt}
\textbf{AutoScene} | PESU Research Foundation \hfill \textbf{June 2025 -- August 2025} \\
\textit{Research Intern, Bangalore} 
\begin{itemize}[leftmargin=1em, itemsep=0em, topsep=0em]
\vspace{-0.4em}
    \item Automated 3D feature extraction achieved, achieving 70-73\% IoU on building and road segmentation by fine-tuning state-of-the-art models.
    \vspace{-0.2em}
    \item Built a pipeline in Python to generate georeferenced vector maps and 3D urban models using segmentation outputs and depth estimation/DEM.
    \vspace{-0.2em}
\end{itemize}


% --- Projects ---
\textbf{PROJECTS}
\vspace{3pt}
\hrule
\vspace{1pt}
\textbf{\href{https://github.com/sanjiv-raghunandan/PlagDetect}{HyperCluster}}%
\vspace{-0.4em}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Engineered a decentralized framework for collaborative AI in Python by sharding standard Hugging Face Transformer models across devices in an Iroh P2P network.
    \item Implemented a ring-based pipeline with distributed node-local KV caching to optimize bandwidth and successfully ran inference on Llama-3.2 1B and Qwen3 0.6B on CPU-only consumer devices.
    \item Authored a research paper accepted for poster presentation at the AAAI 2026 ML4Wireless Workshop.
\end{itemize}
\vspace{-0.4em}
\textbf{\href{https://github.com/sanjiv-raghunandan/PlagDetect}{PlagDetect}}%
\vspace{-0.4em}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Built a plagiarism detection system in Java, applying the MVC pattern with JavaFX for UI, JDBC for database integration, and Gradle for the build tool.
    \item Worked with a team of four and integrated JPlag to compare and analyze code similarity across large datasets with 1000+ files, achieving 83-90\% accuracy.
\end{itemize}
\vspace{-0.4em}
\textbf{\href{https://github.com/sanjiv-raghunandan/Raft3D}{Raft3D}}%
\vspace{-0.4em}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Developed a distributed key-value store and 3D print job manager in Go, implementing the Raft consensus algorithm for fault tolerance and consistency.
    \item Worked with a team of four and implemented a RESTful API for system management.
\end{itemize}
\vspace{-0.4em}
\textbf{\href{https://github.com/sanjiv-raghunandan/Permissioned-blockchain-Patient-record-management}{MedChain}}%
\vspace{-0.4em}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Designed a decentralized application with React, Solidity, and IPFS to securely manage medical records on the Sepolia testnet.
    \item Worked with a team of four and implemented role-based access control with MetaMask to ensure privacy and integrity.
\end{itemize}

% --- Certifications ---
\textbf{CERTIFICATIONS}
\vspace{3pt}
\hrule
\vspace{1pt}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \item Hackkerank Problem Solving Certification
    \item AI Python for Beginners
\end{itemize}

\end{document}